Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-05-09 2016-Weak-FH-Bisim/WeakBisim.tex
corrections notations

Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
directly ($\alpha_x$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\end{mathpar}
\item Concerning the middle open transition in $\mathcal{T}_1$, we have:
 \begin{mathpar}
     \openrule
         {
           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha} s_{21}} 
\end{mathpar}
For each of the weak open transition obtained above, we have  $(s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$  and $s_{11}=s_{20}$, so we have  $(s_{20},t_x|\Pred_{s_{20},t_x})\in \mathcal{R}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
\end{mathpar}
 such that  $\forall x,\forall y, J_{xy}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
(s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},t_x} \land \Pred_2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
 \!\!  \left( \forall j\in J_{x y}. \vis{\beta_{2j}}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
     \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}}\right)$

@@

   ( \forall j\in J_{x y}. \vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \\ \Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\! \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}})\Big)\subst{\Post_1\uplus\Post_{OT_x}} \Big)$\\
Furthermore, the rewriting of the formula  gives:\\

@@

\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\uplus \Post_{OT_x}}\Big)$\\ 

@@

\Big(\forall j\in J_x. \vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\uplus \Post_{OT_x}}\Big)$\\ 

@@

\tau \land \alpha\!=\! \alpha_{x y} \subst{\Post_{OT_x}} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 

@@

\tau \!\land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}}\land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\shortotimes \,\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\

@@

@@

\Big(\forall j\in J_{x y z}. \vis{\beta^1_j}.\vis{\beta_{2j}}\subst{\Post_{OT_x}}.\vis{\beta_{3j}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \!=\!\gamma_{j x y z} \Rightarrow  \Pred_{OT_x}\land\Pred_{OT_{x y}}\subst{\Post_{OT_x}} \land \Pred_{OT_{x y z}}\subst{\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \land \alpha\!=\!\alpha_{x y}\subst{\Post_{OT_x}} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\shortotimes\Post_{OT_{x y z}}\shortotimes\Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\
 \TODO{gamma ne me convainc pas et je dois generaliser}
This is exactly what we needed to prove. \qed

>>>>

Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
directly ($\alpha_x$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
         {t \OTWeakarrow {\tau} t_x}
\end{mathpar}
\item Concerning the middle open transition in $\mathcal{T}_1$, we have:
 \begin{mathpar}
     \openrule
         {
           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha} s_{21}} 
\end{mathpar}
For each  weak open transition obtained above, we have  $(s_{11},t_x|\Pred_{s_{11},t_x})\in \mathcal{R}$  and $s_{11}=s_{20}$, so we have  $(s_{20},t_x|\Pred_{s_{20},t_x})\in \mathcal{R}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{x y}^{x\in X,y\in Y} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j x y}^{j\in J_{x y}}, \Pred_{OT_{x y}},\Post_{OT_{x y}}}
         {t_x \OTWeakarrow {\alpha_{x y}} t_{x y}}
\end{mathpar}
 such that  $\forall x,\forall y, J_{xy}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
(s_{21},t_{x y}|\Pred_{s_{21},t_{x y}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},t_x} \land \Pred_2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{y\in Y}}
 \!\!  \left( \forall j\in J_{x y}. \vis{\beta_{2j}}\!=\!\gamma_{jx y}\Rightarrow \Pred_{OT_{x y}}\!\land \alpha\!=\!\alpha_{x y} \land  
     \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}}\right)$

@@

    \forall j\in J_{x y}. \vis{\beta_{2j}}\!\!=\!\!\gamma_{jx y} \\ \Rightarrow \Pred_{OT_{x y}}\land \alpha\!=\!\alpha_{x y}\! \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\uplus\Post_{OT_{x y}}}\Big)\subst{\Post_1\uplus\Post_{OT_x}} \Big)$\\
Furthermore, the rewriting of the formula  gives \TODO{ajouter argument $\alpha\!=\!\alpha_{x y} \subst{\Post_1\uplus\Post_{OT_x}}$ et $\vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}$}:\\

@@

\Big(\forall j\in J_x. \vis{\beta_{1j}}\!\!=\!\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\subst{\Post_1\uplus\Post_{OT_x}} \!=\!\gamma_{jx y}  \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_1\uplus\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_1\uplus\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\ 

@@

\Big(\forall j\in J_x. \vis{\beta_{1j}}\!=\!\gamma_{jx} \land  \forall j \in J_{x y}. \vis{\beta_{2j}}\subst{\Post_{OT_x}}\!=\!\gamma_{jx y}   \Rightarrow\Pred_{OT_x} \land  \Pred_{OT_{x y}} \subst{\Post_{OT_x}} \land \alpha_x\!=\!\tau \land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}} \land \Pred_{s_{21},t_{x y}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{x y}}\shortotimes \Post_{OT_x}}\Big)$\\ 

@@

\tau \land \alpha\!=\! \alpha_{x y} \subst{\Post_{OT_x}} \land (\Pred_{s_{21},t_{xy}} \land  \Pred_3) \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{x y}}\shortotimes\Post_{OT_x}} \Big)$\\ 

@@

\tau \!\land \alpha\!=\!\alpha_{x y} \subst{\Post_{OT_x}}\land \alpha_{x y z}\!=\!\tau \land \Pred_{s_{31},t_{x y z}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{x y z}}\shortotimes \Post_{OT_{x y}}\shortotimes\Post_{OT_x}}_{\Post}} \Big)$\\

@@

$\Pred_{s,t} \land \Pred_{OT}\\

@@

\Big(\forall j\in J_{x y z}. \gamma_j =\gamma_{j x y z} \Rightarrow  \Pred \land \alpha =\alpha_{x y}\subst{\Post_{OT_x}} \land \Pred_{s',t_{x y z}}\subst{\Post_{OT}\uplus \Post} \Big)$\\
 This is exactly what we needed to prove \TODO{je dois generaliser}. \qed
